manuscript

### 2025-01-31 doc/Manuscript.qmd
continue introduction

The well-documented decline of the endangered Sierra Nevada yellow-legegd frog in its namesake mountain range of California (bunch of citations) is emblematic of the crisis facing amphibians globally (citations). As is the case with numerous other species..the fungal pathogen Bd is the primary driver of SNYLF decline in the Sierra Nevada (citations), and the effects of climate change loom large, especially in an alpine environment expriencing accelerated climate change (mountain ranges are warming faster than other places?) (citation).

@@

To successfully leverage these disease-persistent populations as a conservation resource, we must gain a detailed understanding of their demographics, dynamics, and the factors that influence their viability. Without good information, we can't make smart decisions and we will waste limited resources (Brown xxxx).

The population we focus on in this study-Mossy Pond-provides an excellent opportunity to fill the void of information surrounding this species in the northern portion of its range (cite interagency 2018 and Brown). Weird habitat, funky frogs, and little knowledge, etc..

In this investigation we set out to estimate demographic parameters (getting absolute abundance is really important, as Os for citations on that) and to investigate the rolethat climate plays in population viability. Ultimately, we hope our insights are useful for the management of this paprticualr population, for a deeper understanding of the species as a whole, and as a hint of how climate change may affect alpine amphibian populations in the future.

>>>>

The well-documented decline of the endangered Sierra Nevada yellow-legegd frog in its namesake mountain range (bunch of citations) is emblematic of the crisis facing amphibians globally (citations). As is the case with numerous other species...the fungal pathogen Bd is the primary driver of SNYLF decline in the Sierra Nevada (citations), and the effects of climate change loom large-yet remain understudied- especially in an alpine environment expriencing accelerated climate change (mountain ranges are warming faster than other places?) (citation).

@@

To successfully leverage these disease-persistent populations as conservation resources, we must gain a detailed understanding of their demographics, dynamics, and the factors that influence their viability. Without good information, we can't make smart decisions and we will waste limited resources (Brown xxxx).

The population we focus on in this study-Mossy Pond-provides an excellent opportunity to fill the void of information around disease-persistent populations of this species in the northern portion of its range (cite interagency 2018 and Brown). Pop description: Weird habitat, funky frogs, and little knowledge, etc.. Complexity of habitat here is representative of northern pops generally: streams, complexity, etc.

In this investigation we set out to estimate demographic parameters (getting absolute abundance is really important, as Os for citations on that) and to investigate the (factors that influence population viability in the Bd-persistent state) (role that climate plays in population viability). Ultimately, we hope our insights are useful for the management of this paprticualr population, for a deeper understanding of the species as a whole, and as a hint of how climate change may affect alpine amphibian populations in the future.
